TODO: title

### 2014-04-23 paper/main.tex
more work on results.

  This result is rather strange as MAP and precision are metrics where high scores are good, where fallout is a metric where high scores are bad.
  This leads to an issue, these metrics contradict each other in terms of the quality of the recommendations from our algorithm.
  One possible reason for this is that these topN metrics are known to be biased by popular items (TODO: cite bellogin).
  Looking at the average popularity (figure \ref{fig:pop})of recommended items, we see that this seems to explain most of the variance in these metrics.
  Therefore we seek a different metric to analyze the quality of the recommendations.

  Figure \ref{fig:topN.rmse}
    % TopN average rating / topn rmse
    % interpret graph and reason about what it means about quality
  % Other recommender metrics
    % popularity graph
    % diversity plot
    % talk about popularity and diversity
      % algos don't cross, and seem more straight, this seems to be more of a system wide choice than other metrics.***
      % relatively the same thing as each other.
      % upward diversity trend in baselines - seen items removed from recs => must increase diversity
      % we don't know best, but user user is probably too bad, and avg rating is probably too high SVD and Item-Item probably in a good zone.
      % user study would be needed to find out.
    % spread plot
      % by and far item-item has the best spread
      % user-user has good spread, but interestingly the spread gets worse
        % not sure why, perhaps as more ratings there is a regression to the mean sort of trend where more ratings means mroe neighbors available, means more ratings.
        % either way we don't see this as a good thing...
      % svd
        % spread seems a little low. like before we don't _know_, but it looks like svd might focus too much on a smaller list of items.
\section{Conclusions}
  % summary of results in a big old table.
    % the accuracy of svd and user-user both seemed good. item-item seemed to have trouble especially with very new users.
    % svd did quite well on our traditional topN metrics, item-item did OK, and user-user did bad., but there are flaws with these metrics.
    % on our topN RMSE item-item (again) seemed to have issues, and user-user did quite well, but the low hit rate is troubleing. 
    % again svd seems the winner here.
    % on our fluffy metrics item-item and svd seemed to do well. I might argue that item-item seemed to do better (spread, and higher throughout).
    % user-user seemed to do poor
  % what this means
    % user-user seems to be able to give accurate predictions, but seems to focus on overly obscure items in recommendation.
    % item-item seems to give not-bad recommendations, but its predictions have issues
    % based only on these results svd seems to be the best performer and is our recommendation to new systems.
  % other takeaways
    % regularization
    % if you use a switching recommender, this methodology can help you choose when to switch.
    % non-traditional metrics can tell you more about what is going on, these seem to be more properties of the class of algo than of the data, so its worth looking at these when choosing algorithms, to find one with properties that are good for your task.

@@

\section{Acknowledgements}
 \cite{harper2005economic}
 TODO:

>>>>

  This result is rather strange as MAP and precision are metrics where high scores imply better performance, whereas fallout is a metric where high scores imply poor performance.
  This leads to an issue, these metrics contradict each other in terms of the quality of the recommendations from our algorithm.
  One possible reason for this is that these topN metrics are known to be biased toward recommendations that have more popular items \cite{bellogin}.
  Looking at the average popularity (figure \ref{fig:pop}) of recommended items, we see that the average popularity of the recommendations closely replicates the previous three plots.
  Therefore we seek a different, less biased metric to analyze the quality of the recommendations.

  % TopN average rating / topn rmse
    % interpret graph and reason about what it means about quality
  The first graph in figure \ref{fig:topN.rmse} shows the average number of items in the top 20 recommendations for each algorithm that were also in the test set.
  The average number of test set items in recommendations shows a similar trend to the MAP, precision, and recall metrics, user-user getting by far the fewest seen items, and the baseline getting the most.
  %TODO: talk about trust building here!

  The second graph in figure \ref{fig:topN.rmse} shows the average rating for those items in the top 20 recommendations for each algorithm.
  The first thing to note about this graph is that all of these algorithms are doing a reasonable job of recommending items the user might like to watch, with all algorithms averaging above 4 stars (implying that the recommended items are, at least on average, enjoyable).
  SVD performs as expected, starting at close to the same average rating as the baselines, and then slowing improving as more ratings are entered.
  Item-Item performs poorly, not only performing worse than the baseline, but showing worse performance as more ratings are added.
  This is quite possibly a similar trend to the one we observed with RMSE and nDCG, where Item-Item's performance decreased as coverage increased leading to the curved performance at cold start.

  During testing with other values of N for this metric and the next, we found that User-User's behavior compared to the other algorithms changed significantly with different values of N.
  This is probably due to the very low rate of having seen items in the recommendations, which makes its value much less stable, than the other algorithms.
  Because of this behavior we will draw no conclusion from User-User's performance on this metric, to avoid accidentally attributing behavior to it, that was instead formed by our choice of 20 as N.

  The third graph in figure \ref{fig:topN.rmse} shows the RMSE our algorithms got on items in the top 20 recommendations for each algorithm.
  Not surprisingly, this figure shows the same trends as the last one meaning that the algorithms whose recommendations were (on average) most likable, were those whose recommendations were most accurate.
  Again, SVD performs quite well, Item-Item shows poor performance, and, due to sensitivity of User-User to our choice of N, we make no conclusions about User-User.

\subsection{Other recommender metrics}
  % Other recommender metrics
  Figure \ref{fig:pop} shows the

    % popularity graph
    % diversity plot
    % talk about popularity and diversity
      % algos don't cross, and seem more straight, this seems to be more of a system wide choice than other metrics.***
      % relatively the same thing as each other.
      % upward diversity trend in baselines - seen items removed from recs => must increase diversity
      % we don't know best, but user user is probably too bad, and avg rating is probably too high SVD and Item-Item probably in a good zone.
      % user study would be needed to find out.
    % spread plot
      % by and far item-item has the best spread
      % user-user has good spread, but interestingly the spread gets worse
        % not sure why, perhaps as more ratings there is a regression to the mean sort of trend where more ratings means mroe neighbors available, means more ratings.
        % either way we don't see this as a good thing...
      % svd
        % spread seems a little low. like before we don't _know_, but it looks like svd might focus too much on a smaller list of items.
\section{Conclusions}
  % summary of results in a big old table.
    % the accuracy of svd and user-user both seemed good. item-item seemed to have trouble especially with very new users.
    % svd did quite well on our traditional topN metrics, item-item did OK, and user-user did bad., but there are flaws with these metrics.
    % on our topN RMSE item-item (again) seemed to have issues, and user-user did quite well, but the low hit rate is troubleing. 
    % again svd seems the winner here.
    % on our fluffy metrics item-item and svd seemed to do well. I might argue that item-item seemed to do better (spread, and higher throughout).
    % user-user seemed to do poor
  % what this means
    % user-user seems to be able to give accurate predictions, but seems to focus on overly obscure items in recommendation.
    % item-item seems to give not-bad recommendations, but its predictions have issues
    % based only on these results svd seems to be the best performer and is our recommendation to new systems.
  % other takeaways
    % regularization
    % if you use a switching recommender, this methodology can help you choose when to switch.
    % non-traditional metrics can tell you more about what is going on, these seem to be more properties of the class of algo than of the data, so its worth looking at these when choosing algorithms, to find one with properties that are good for your task.

@@

\section{Acknowledgements}
 TODO:
